Web Scraping: attempt 2

### 2017-04-11 Web_Scraping_Final.Rmd
Fix small thing in short function. Now in terms of "MSP" instead of "DSM"

```{r}
library(beepr)
library(tidyverse)
library(rvest)
dates_all <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), 
                                                                 to = as.Date("2017-03-31"), by = "days"))
links_all <- paste0(dates_all, "/DailyHistory.html")

@@

airport <- "KDSM"
DSM_daily <- data.frame(Links = links_all)  
DSM_daily <- DSM_daily %>% nest() %>% 
  mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
                  select(-Links) %>% unnest(data) %>% unnest(daily_temps) %>% as.data.frame()
beepr::beep(8)
```

@@

grab_ave_rec_temps <- function(link, airport){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0("KDSM/", link))
  html <- read_html(ss)

@@

airport <- "KDSM"
DSM_ave_rec <- data.frame(Links = links_2016)  
DSM_ave_rec <- DSM_ave_rec %>% nest() %>% 
  mutate(ave_rec_temps = Links %>% purrr::map2(., airport, grab_ave_rec_temps)) %>% 
  select(-Links) %>% unnest(data) %>% unnest(ave_rec_temps) %>% as.data.frame()

@@

*put two datasets together and add some elements*
```{r}
head(DSM_daily)
#names(DSM_daily) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
head(DSM_ave_rec)
#names(DSM_ave_rec) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
DSM_temps <- rbind(DSM_daily, DSM_ave_rec)

DSM_temps <- DSM_temps %>% mutate(airport = airport)
DSM_temps <- DSM_temps %>% mutate(city = "Des Moines, IA") # change this each time

DSM_temps <- DSM_temps %>% mutate(day = lubridate::day(date),
                                  month = lubridate::month(date),
                                  year = lubridate::year(date))
```

*save final dataset*
```{r}
save(DSM_temps, file = "raw-data/DSM_temps.csv")
```

>>>>

```{r}
library(beepr)
library(tidyverse)
library(rvest)
dates_all <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1948-01-01"), 
                                                                 to = as.Date("2017-03-31"), by = "days"))
links_all <- paste0(dates_all, "/DailyHistory.html")

@@

airport <- "KMSN"
MSN_daily <- data.frame(Links = links_all)  
MSN_daily <- MSN_daily %>% nest() %>% 
  mutate(daily_temps = Links %>% purrr::map2(., airport, grab_act_temps)) %>%
                  select(-Links) %>% unnest(data) %>% unnest(daily_temps) %>% as.data.frame()
beepr::beep(8)
```

@@

grab_ave_rec_temps <- function(link, airport){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0(airport, "/", link))
  html <- read_html(ss)

@@

airport <- "KMSN"
MSN_ave_rec <- data.frame(Links = links_2016)  
MSN_ave_rec <- MSN_ave_rec %>% nest() %>% 
  mutate(ave_rec_temps = Links %>% purrr::map2(., airport, grab_ave_rec_temps)) %>% 
  select(-Links) %>% unnest(data) %>% unnest(ave_rec_temps) %>% as.data.frame()

@@

*put two datasets together and add some elements*
```{r}
head(MSN_daily)
#names(DSM_daily) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
head(MSN_ave_rec)
#names(DSM_ave_rec) <- c("date", "mean_max_min", "actual_ave_rec", "value") # just one fix, already fixed in other code
MSN_temps <- rbind(MSN_daily, MSN_ave_rec)

MSN_temps <- MSN_temps %>% mutate(airport = airport)
MSN_temps <- MSN_temps %>% mutate(city = "Madison, WI") # change this each time

MSN_temps <- MSN_temps %>% mutate(day = lubridate::day(date),
                                  month = lubridate::month(date),
                                  year = lubridate::year(date))
```

*save final dataset*
```{r}
write.csv(MSN_temps, file = "raw-data/MSN_temps.csv")
```
